Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-19 paper/example.tex
Fix minor typos
Slight cleanup in overview-of-BriefCASE section

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{flowchart.png} \\
    \end{tabular}
  \end{center}
\caption{Simplified \brfcs\ workflow with the contributions detailed in this manuscript shaded.}
\label{fig:flowchart}
\end{figure*}

@@

\figref{fig:flowchart} illustrates a simplified \brfcs\ workflow with the shaded boxes representing the contributions discussed in this manuscript: test contracts, code contracts, and SPLAT synthesis.
The unshaded boxes are the existing tools that generate evidence for the assurance case.
The rest of this section follows an illustrative example through the workflow.

The baseline AADL model is a simple software system, named SW, for route planning
and automated control of a UAV. A picture of the architectural
model for SW is in \figref{fig:example}. SW is loosely based on one of
the case studies in Section~\ref{sec:case-study}.  The source for the
entire model is found at \cite{repo}.

@@

Extending the \agr\ verification results to the system composition requires additional guarantees not discussed in this manuscript.
For example, among other things, contracts for non-synthesized components must be certified to accurately model their deployed counterparts, the HAMR generated scheduler must be certified to follow the dependent data-flow in the design, scheduling windows must be certified to cover worst-case execution times, etc.
Such additional guarantees are discussed in other works \cite{gearcase2020, dcrypps2019, 10.1007/978-3-030-89159-6_18, 10.1007/978-3-030-89159-6_17, sel4-2009, scheduled-agree, 9734792}.

>>>>

\begin{figure*}
  \begin{center}
    \begin{tabular}{c}
      \includegraphics[scale=0.4]{flowchart.png} \\
    \end{tabular}
  \end{center}
\caption{Simplified \brfcs\ workflow. Shaded portions are the focus of the present discussion.}
\label{fig:flowchart}
\end{figure*}

@@

\figref{fig:flowchart} illustrates a simplified \brfcs\ workflow with the shaded boxes representing our focus: test contracts, code contracts, and SPLAT synthesis.
The unshaded boxes are the existing tools that generate evidence for the assurance case.
The rest of this section follows an illustrative example through the workflow.

The baseline AADL model is a simple software system, named SW, for route planning
and automated control of a UAV. A picture of the architectural
model for SW is in \figref{fig:example}. SW is loosely based on
the case study in \secref{sec:case-study}.  The source for the
entire model is found at \cite{repo}.

@@

Extending the \agr\ verification results to the system composition
requires additional guarantees not discussed here.  For
example, among other things, contracts for non-synthesized components
must be certified to accurately model their deployed counterparts, the
HAMR generated scheduler must be certified to follow the dependent
data-flow in the design, scheduling windows must be certified to cover
worst-case execution times, \etc.  Such additional guarantees are
discussed in other works \cite{gearcase2020, dcrypps2019,
  10.1007/978-3-030-89159-6_18, 10.1007/978-3-030-89159-6_17,
  sel4-2009, scheduled-agree, 9734792}.

### 2022-09-19 paper/overview.tex
Slight cleanup in overview-of-BriefCASE section

The \brfcs\ OSATE environment, \figref{fig:tool-arch}, provides designers with workflow and tool support for developing products with inherent cyber-resiliency.
It starts with the development of a baseline AADL model of the system architecture that defines the desired functionality.
This model can be evaluated using existing tools such as resource usage, information flow, latency analysis, etc. for validation.

@@

Important to the contributions presented in this paper is the Assume Guarantee Reasoning Environment (\agr) \cite{compositional-analysis-agree,nfm:agree}. It is a compositional, assume-guarantee-style, model checker for AADL models. 
\agr\ attempts to prove properties about one layer of the model using properties allocated to sub-components.
The composition is performed in terms of \emph{contracts} provided for each component and sub-component that state \emph{assumptions} on inputs and \emph{guarantees} on outputs under the assumptions.
\agr\ verifies the \emph{consistency} of the composition of the component and sub-component contracts meaning that in every connection the source constraints satisfy the destination constraints.

The contributions discussed in this paper relate to the aspects of \brfcs\ concerning evidence that a high-assurance component meets its intended purpose and is properly implemented.
This paper defines a \emph{code contract} language that is a subset of the \agr\ language with sequential evaluation semantics as opposed to the existing parallel semantics of \agr.
The sequential semantics are requisite to code synthesis and are defined such that \agr\ is able to still prove consistency in the contract composition of the model.

This paper further defines a stylized \emph{test contract} for unit testing code contracts outside of the system composition to verify input to output behavior as well as general properties of the code contract.
As such, the behavior of a high assurance component is defined by the designer in a code contract, and then using the existing \agr\ model checker, test contracts prove the desired code contract behavior.
Once the designer is satisfied that the code contract is correct, the system composition is verified to conclude that the contract meets its intended purpose.

Showing that a component is properly implemented is accomplished through formal synthesis from the code contract (bottom of \figref{fig:tool-arch}).
This paper presents the Semantic Properties of Language and Automata Theory (\splt) tool that generates \emph{\ckml} code to implement the code contract.
\ckml\ is a functional language that includes additional proofs and tools built around it \cite{cakeml}.
The \ckml\ compiler itself is verified to generate binary implementations that are equivalent in semantics to the original input program.
That proof ensures that the resulting binary exactly preserves the meaning of the original code contract and assures that the component is properly implemented.

>>>>

The \brfcs\ OSATE environment, \figref{fig:tool-arch}, provides
designers with workflow and tool support for developing products with
inherent cyber-resiliency.  It starts with the development of a
baseline AADL model of the system architecture that defines the
desired functionality.  This model can be evaluated on aspects such as
resource usage, information flow, latency analysis, {\etc} using
existing tools.

@@

As mentioned earlier,
\agr\ \cite{compositional-analysis-agree,nfm:agree} provides the
formal platform for our work. It bundles together a formal contract
language with a compositional, assume-guarantee-style, model checker
for AADL models.  \agr\ attempts to prove properties about one layer
of the model using properties allocated to sub-components.  The
composition is performed in terms of \emph{contracts} provided for
each component and sub-component that state \emph{assumptions} on
inputs and \emph{guarantees} on outputs under the assumptions.
\agr\ verifies the \emph{consistency} of the composition of the
component and sub-component contracts meaning that in every connection
the source constraints satisfy the destination constraints.

The contributions of this paper relate to the aspects of
\brfcs\ concerning evidence that a high-assurance component meets its
intended purpose and is properly implemented.  This paper defines a
\emph{code contract} language that is a subset of the \agr\ language
with sequential evaluation semantics as opposed to the existing
parallel semantics of \agr.  The sequential semantics are requisite to
code synthesis and are defined such that \agr\ is able to still prove
consistency in the contract composition of the model.

This paper further defines a notion of \emph{test contract} for unit
testing code contracts outside of the system composition to verify
input to output behavior as well as general properties of the code
contract.  In practice, the behavior of a high assurance component is
defined by the designer in a code contract, and then using the
existing \agr\ model checker, test contracts prove the desired code
contract behavior.  Once the designer is satisfied that the code
contract is correct, the system composition is verified to conclude
that the contract meets the original cyber-requirement.

Showing that a component is properly implemented is accomplished
through formal synthesis from the code contract (bottom of
\figref{fig:tool-arch}).  This paper presents the Semantic Properties
of Language and Automata Theory (\splt) tool that generates
\emph{\ckml} code to implement the code contract.  \ckml\ is a
functional language that includes additional proofs and tools built
around it \cite{cakeml}.  The \ckml\ compiler itself is verified to
generate binary implementations that are equivalent in semantics to
the original input program.  That proof ensures that the resulting
binary exactly preserves the meaning of the original code contract and
assures that the component is faithfully implemented.
